Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-08-29 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd

## Comments from reviewer #2

*The manuscript by C Wang et al includes a cohort of 94385 men and women from Japan, free from self-reported history of stroke, cancer, myocardial infarction and other types of heart disease at baseline who answered an FFQ regarding milk consumption. Between baseline in 1988-90 and end of follow-up in 2009, 2675 deaths from stroke were recorded on death registers. The authors applied Bayesian survival analysis to calculate hazard ratios and acceleration factors. With a range of milk consumption from “never” to “almost daily”, a higher milk consumption was associated with lower hazard and speed from dying from total stroke among men but not among women.*

*I have the following comments and questions for the authors:*

- *#1: The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution. The dose-response meta-analysis in reference 2 indicates that the association may be non-linear. It would be good if the authors in more detail compared their results with other studies using fatal stroke as outcome and perhaps also focus on those cohorts with a low milk intake. For example, please elaborate on references 6, 20-23 in the discussion. Some of the references do not investigate milk intake per se. In the discussion, please specify that reference 19 does not investigate stroke mortality but CVD and all-cause mortality.*

[Response:] We greatly appreciate the reviewer's points. We have updated the Introduction as well as the Discussion so that we could draw readers' attention to the fact that absolute milk intake of these participants were actually in the lower range of milk intake in the world. We have elaborated the issue in Discussion by comparing our findings with previous studies conducted in East Asian population. We have also clarified the fact that the reference #19 in the previous manuscript (#16 in the revised manuscript) dealt with milk intake in relation to CVD and all-cause mortality.

- *#2: I am unfortunately not familiar with the Bayesian models used in this work. I am sure that many readers will be in a similar situation as me. I appreciate that these models can calculate hazard ratios without fulfilling the proportional hazards assumption. The authors should in more detail describe the benefits and limitations of these models in relation to the more commonly used Cox proportional hazards regression. Is a HR estimated from these models directly comparable with that from a Cox model? How is an acceleration factor interpreted? Do the models assume that a higher milk intake is associated with a lower stroke mortality, indicated also by the Pr(HR<1)? If so, how would that influence the validity of the method since you in the introduction write that there are reports of inverse associations, no association, and direct associations? In Table 2, both SD and 95% CrI are given. Is there a reason for specifying the SD?*

[Response:] Thanks for the frank comments about the Bayesian models and suggestions. We gave more explanations for the methods as well as benifit and background for their use in the revised manuscript. For example, acceleration factor (AF) can be interpreted as the speed/velocity just like all individuals are driving their cars from the same start point (entry into the study setting) to their goals (stroke mortality) but different people can drive their own car with different speeds. If the AF of a certain group is smaller than 1 (i.e., reference group - never drinker), then it is considered that individuals in that group would reach the goal with slower speed (or take longer time). We might be able to argue that the statistic AF would be easier to be interpreted compared with hazard ratios (HR), which often requires several assumptions.

We also realized that not many readers would be familiar with the method employed in the present study. In an attempt to briefly introduce the Bayesian approach to the reviewer, we would like to give our understanding of the traditional Cox proportionla hazard model (or any other classical statistical methods). First, it assumes only one true but unknown value of the parameter (in this context, the HR and AF) is going to be obtained from the data at hand. Second, it assumes that the experiment/study can be repeated. This is fundamental to the calculation of the confidence intervals through the calculation of standard errors so that they can be interpreted as "if we repeat the same experiment for many times, 95% of these confidence intervals will contain the true but unknown value of interest". Third and similarly, a P-value is the probability of observing a certain or more extreme results if an experiment/study can be repeated, which would raise a question that relying on P<0.05 criterion may not be valid if the repeatable assumption is not valid.

Instead of employing the unrealistic repeatable assumption, Bayesian ways of statistical analyses provide a posterior distribution of the parameter of interest. In other words, it estimates the a statistic (e.g., HR, AF, etc.) with a distribution that can be described by its mean and standard deviation. And through which the 95% credible intervals can be presented and be interpreted as we are 95% sure that the parameter of interest is distributed in this range. Although Bayesian approach requires extensive simulations, it provides straightforward results, that is, Pr(HR < 1), the precentages of observed HRs that were smaller than 1.

We would like to emphasize that the statistical models used in the Bayesian approach is the same as that in the traditional approach. Therefore, the meaning of HRs is the same. One and the biggest drawback of the Bayesian approach is the extensive computational cost, which was partly resolved by the recent advancement of personal computers. Nevertheless, we presented results obtained using the Bayesian approaches in the present study since we believe it is more appropriate statistically. We have added these issues in the "strength and limitation" section of the revised manuscript.

- *#3: Why were analyses performed stratified by sex? Since no pooled analysis is presented, the reason for a stratified analysis should be stated in the aims, unless this was a secondary analysis and then also the results from the total cohort should be presented. The authors should also discuss the observed sex differences in more detail. Do other studies show similar sex differences? What potential biological mechanisms may explain them?*

[Response:] Thanks for the pertinent comment. Although we conducted the presenty analyses in men and women separately from the beginning based our previous finding from the same cohort as well as on a prior finding from the Singapre Chinese Health Study, the rationale might not have have been clear. We have revised the manuscript (Methods) incorporating the point. Nevertheless, a test of interaction for milk intake by sex indicated significant interaction (using traditional likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies, P < 0.0001, not shown in the main test). Stratified analyses by sex also suggested the directions of AFs and HRs differ in a few frequency categories (Table 2 and 3, results in the "total stroke" parts).

We have also added possible explanations for the sex-interaction in the Discussion.

- *#4: The aim states to “provide a more straightforward answer to the primary research question” – compared to what? And how is this more straightforward answer achieved. This is not clear, neither in the aim nor in the discussion (lines166-167). Please revise.*

[Response:] Thanks

Thanks for your suggestion. The more straightforward answer is provided as Pr(HR < 1) which shows the percentages of HRs < 1 calculated through the large amount of simulations. The detailed interpretation is described above in answering your second comment. These probabilities show directly how certain it is for individuals with that milk intake frequency could have lower hazard compared with those who never consume milk. In the traditional way the answer was not clear since only estimates of HRs, 95% confidence intervals, and/or P-values were shown. None of these actually can directly answer the question "how sure it is to have lower hazard in one group compared with another?" We have added clearer descriptions about these research questions and interpretations.

### 2020-08-30 Paperfolder/MDPI_submission/Revision01/MDPI_submission/Paperfolder.tex
revision 01 99% done

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort (JACC) Study (total number of
participants = 110585, age range: 40-79) to estimate the posterior
acceleration factors (AF) as well as the hazard ratios (HR) comparing
individuals with different milk intake frequencies against those who
never consumed milk at the study baseline. These estimations were
computed through a series of Bayesian survival models that employed a
Markov Chain Monte Carlo simulation process. 100000 posterior samples
were generated separately through four independent chains after model
convergency was confirmed. Posterior probabilites that daily milk
consumers had lower hazard or delayed mortality from strokes compared to
non-consumers was 99.0\% and 78.0\% for men and women, respectively.
Accordingly, the estimated posterior means of AF and HR for daily milk
consumers were 0.88 (95\% Credible Interval, CrI: 0.81, 0.96) and 0.80
(95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI: 0.88, 1.10) and 0.95
(95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
study has provided strong evidence that daily milk intake among Japanese
men was associated with delayed and lower hazard of mortality from
stroke especially cerebral infarction.}

@@

Eastern Asian populations were reported to have higher burden from both
mortality and morbidity from stroke than populations in European or
American regions \citep{Kim2014}. Dairy foods, especially milk has been
suggested to related with decreased stroke risk by nearly 7\% for each
200 g increment of daily consumption \citep{DeGoede2016}. Although 2
daily servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
Western countries \citep{Saito2019}. Given that previous reports have
also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, it would be of interest to provide
information on the association within a context that most individuals
have much lower range of milk intake compared to most of the previous
studies. Whether people with such a low level intake of milk can still
benefit against stroke would require elucidation.

Moreover, a more intuitive or straightforward interpretation would be
available if we were able to show the probabilities and the certainty
that the existing data can provide evidence about whether drinking milk
can delay or lower the hazard of dying from stroke. This would require
transformation of the research question into ``Do individuals with milk
intake habit have lower hazard of dying from a stroke event?'' Another
way of asking the same research question would be ``Can a event of dying
from stroke be postponed by having a milk intake habit?'' The later
question is indeed directly comparing the length of times before events
or the speed from the same departure point (entry of the study) to a
fatal stroke event. Accelerated failure time models (AFT) under Bayesian
framework are convenient tools that would help avoid worrying about the
assumptions of repeatability of a large scale prospective study, and can
calculate the exact proportion of posterior estimates (hazard ratios,
HR) that is lower than 1. AFT model is helpful in estimating
acceleration factors (AF) which can be interpreted as the velocity for
developing an event of interest. This velocity parameter shows how
faster/slower individuals in one exposure group might have an event
compared to others in different exposure groups
\citep{Wei1992, ibrahim2014b}.

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and medical histories
of cardiovascular disease or cancer. In the final follow-up of the JACC
study, data from a total of 110585 individuals (46395 men and 64190
women) who aged between 40-79 at the baseline year were successfully
retained for the current analysis. We further excluded samples if they
meet one of the following criteria: 1) with any disease history of
stroke, cancer, myocardial infarction, ischemic heart disease, or other
types heart disease (n = 6655, 2931 men and 3724 women); 2) did not
answer the question regarding their milk consumption in the baseline FFQ
survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men
and 54999 women) are left in the database. The study design and informed
consent procedure were approved by the Ethics Review Committee of
Hokkaido University School of Medicine.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (SD =
0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85, 1.02)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month

@@

\noindent was higher than 86.5\% in men and greater than 94.6\% in
women. However, lower hazard and delayed time-to-event was observed to
remain after age or multivariable adjustment only among daily male milk
consumers. Specifically, the mean (SD; 95\% CrI) of posterior
multivariable-adjusted AF and HR for daily male consumers of milk were
0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95\% CrI:
0.69, 0.93) with a probability of 99.0\% to be smaller than the null
value (=1). Daily female milk consumers had posterior AFs and HRs that
were distributed with means of 0.97 (SD = 0.09; 95\% CrI: 0.88, 1.10)
and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17) which had about 78.0\% of
chance that their HRs could be smaller than 1.

@@

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently life habits are
possible to alter over time and these would result in misclassfication
and residual confoundings. Second, despite reasonable validity of FFQ in
the JACC study cohort was assessed and confirmed, measurement errors are
inevitable. Therefore, we did not try to compute the amount of
consumption by multiplying an average volume per occasion with the
frequency of intake since the random error might be exaggerated and the
observed associations may have attenuated. Third, the Bayesian way of
conducting the survival analysis using a large sample size is
computationally expensive. However, the classic maximum likelihood
estimations are based on unrealistic assumptions such as repeatability
of the study and fixed but unknown values of parameters which are
unfulfilled in a large cohort study in the current setting. Strengths of
our analyses included that we have transformed the research questions to
more transparent ones that is easier for interpretation. Direct
probabilities that daily milk intake is associated with lower hazard or
delayed stroke mortality event were provided here after thorough
computer simulations.

@@

In conclusion, the JACC study database has provided evidence that
Japanese men who consumed milk daily had lower hazard of dying from
stroke particularly cerebral infarction compared with their counterparts
who never consumed milk. Time before an event of stroke mortality
occurred were slowed down and delayed among men who drank milk
regularly.

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort (JACC) Study (total number of
participants = 110585, age range: 40-79) to estimate the posterior
acceleration factors (AF) as well as the hazard ratios (HR) comparing
individuals with different milk intake frequencies against those who
never consumed milk at the study baseline. These estimations were
computed through a series of Bayesian survival models that employed a
Markov Chain Monte Carlo simulation process. 100000 posterior samples
were generated separately through four independent chains after model
convergency was confirmed. Posterior probabilites that daily milk
consumers had lower hazard or delayed mortality from strokes compared to
non-consumers was 99.0\% and 78.0\% for men and women, respectively.
Accordingly, the estimated posterior means of AF and HR for daily milk
consumers were 0.88 (95\% Credible Interval, CrI: 0.81, 0.96) and 0.80
(95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI: 0.88, 1.10) and 0.95
(95\% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC
study provided strong evidence that daily milk intake among Japanese men
was associated with delayed and lower hazard of mortality from stroke
especially cerebral infarction.}

@@

Eastern Asian populations were reported to have higher burden from both
mortality and morbidity from stroke than populations in European or
American regions \citep{Kim2014}. Dairy foods, especially milk has been
suggested to relate with decreased stroke risk by nearly 7\% for each
200 g increment of daily consumption \citep{DeGoede2016}. Although 2
daily servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
Western countries \citep{Saito2019}. Given that previous reports have
also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, it would be of interest to provide
information on the association within a context that most individuals
have much lower range of milk intake compared to most of the previous
studies. Whether people with such a low level intake of milk can still
benefit against stroke would require elucidation.

Moreover, a more intuitive or straightforward interpretation would be
available if we were able to show the probabilities and the certainty
that the existing data can provide evidence about whether drinking milk
can delay or lower the hazard of dying from stroke. This would require
transformation of the research question into ``Do individuals with milk
intake habit have lower hazard of dying from a stroke event?'' Another
way of asking the same research question would be ``Can a event of dying
from stroke be postponed by having a milk intake habit?'' The later
question is directly comparing the length of times before events or the
speed from the same departure point (entry of the study) to a fatal
stroke event. Accelerated failure time models (AFT) under Bayesian
framework are convenient tools that would help avoid worrying about the
assumptions of repeatability of a large scale prospective study, and can
calculate the exact proportion of posterior estimates (hazard ratios,
HR) that is lower than 1. AFT model is helpful in estimating
acceleration factors (AF) which can be interpreted as the velocity for
developing an event of interest. This velocity parameter shows how
faster/slower individuals in one exposure group might have an event
compared to others in different exposure groups
\citep{Wei1992, ibrahim2014b}.

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was
sponsored by the Ministry of Education, Sports, Science, and Technology
of Japan. Sampling methods and details about the JACC study have been
described extensively in the literature
\citep{Ohno2001, Tamakoshi2005, Tamakoshi2013}. Participants of the JACC
study completed self-administered questionnaires about their lifestyles,
food intake (food frequency questionnaire, FFQ), and medical histories
of cardiovascular disease or cancer. In the final follow-up of the JACC
study, data from a total of 110585 individuals (46395 men and 64190
women) who aged between 40-79 at the baseline were successfully retained
for the current analysis. We further excluded samples if they meet one
of the following criteria: 1) with any disease history of stroke,
cancer, myocardial infarction, ischemic heart disease, or other types
heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the
question regarding their milk consumption in the baseline FFQ survey (n
= 9545, 3593 men and 5952 women). Finally, 94385 (39386 men and 54999
women) are left in the database. The study design and informed consent
procedure were approved by the Ethics Review Committee of Hokkaido
University School of Medicine.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable-adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had slower speed and lower hazard of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke was slowed down by a crude acceleration factor (AF) between 0.79
(SD = 0.05; 95\% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95\% CrI: 0.85,
1.02) compared with non-consumers. Chan-

@@

\noindent  ces that the posterior crude HRs were estimated to be lower
than 1 for those who had at least 1-2 times/month was higher than 86.5\%
in men and greater than 94.6\% in women. However, lower hazard and
delayed time-to-event was observed to remain after age or multivariable
adjustment only among daily male milk consumers. Specifically, the mean
(SD; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
male consumers of milk were 0.88 (SD = 0.05; 95\% CrI: 0.81, 0.96) and
0.80 (SD = 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
be smaller than the null value (=1). Daily female milk consumers had
posterior AFs and HRs that were distributed with means of 0.97 (SD =
0.09; 95\% CrI: 0.88, 1.10) and 0.95 (SD = 0.12; 95\% CrI: 0.80, 1.17)
which had about 78.0\% of chance that their HRs could be smaller than 1.

@@

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently life habits are
possible to alter over time and these would result in misclassification
and residual confounding. Second, despite reasonable validity of FFQ in
the JACC study cohort was assessed and confirmed, measurement errors are
inevitable. Therefore, we did not try to compute the amount of
consumption by multiplying an average volume per occasion with the
frequency of intake since the random error might be exaggerated and the
observed associations may have attenuated. Third, the Bayesian way of
conducting the survival analysis using a large sample size is
computationally expensive. However, the classic maximum likelihood
estimations are based on unrealistic assumptions such as repeatability
of the study and fixed but unknown values of parameters which are
unfulfilled in a large cohort study in the current setting. Strengths of
our analyses included that we have transformed the research questions to
more transparent ones that is easier for interpretation. Direct
probabilities that daily milk intake is associated with lower hazard or
delayed stroke mortality event were provided here after thorough
computer simulations.

@@

In conclusion, the JACC study database has provided evidence that
Japanese men who consumed milk daily had lower hazard of dying from
stroke particularly cerebral infarction compared with their counterparts
who never consumed milk. Time before an event of stroke mortality
occurred were slowed down among men who drank milk regularly.
